% Main tex file for DRM paper for KDD 2019

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables


% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[KDD'19]{ACM KDD}{August 2019}{Anchorage, Alaska USA}
\acmYear{2019}
\copyrightyear{2019}

% \acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\editor{Thuc Duy Le, Jiuyong Li, Kun Zhang, Emre K{\i}c{\i}man, Peng Cui, and Aapo Hyv\"{a}rinen}

% path for graphics
\graphicspath{ {figures/} }

\begin{document}
\title{Improve User Retention with Causal Learning}

\author{Shuyang Du}
\affiliation{%
  \institution{Uber, Inc.}
  \streetaddress{1455 Market St}
  \city{San Francisco}
  \state{California}
  \country{USA}
}
\email{shuyangdu@uber.com}

\author{James Lee}
\affiliation{%
  \institution{Uber, Inc.}
  \streetaddress{1455 Market St}
  \city{San Francisco}
  \state{California}
  \country{USA}
}
\email{jameslee@uber.com}

\author{Farzin Ghaffarizadeh}
\affiliation{%
  \institution{Uber, Inc.}
  \streetaddress{1455 Market St}
  \city{San Francisco}
  \state{California}
  \country{USA}
}
\email{farzin@uber.com}

% % The default list of authors is too long for headers.
% \renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
User retention is a key focus for consumer based internet companies and promotions are an effective lever to improve retention. However, companies rely either on non-causal churn prediction to capture heterogeneity or on regular A/B testing to capture average treatment effect. In this paper, we propose a heterogeneous treatment effect optimization framework to capture both heterogeneity and causal effect.

We propose two algorithms to maximize heterogeneous treatment effect: 1) Ranking based on point estimates of heterogeneous treatment effects obtained using existing estimation methods with training labels adjusted based on Lagrangian Subgradient method. 2) A novel ranking algorithm which combines estimation and optimization in one stage and directly optimizes for the aggregated targeted treatment effect.

We also develop an evaluation metric that captures the real-world business value of different methods and use this to evaluate various approaches on our large-scale experiment data set both offline and online. Our algorithm (approach 2) performs significantly better than random explore benchmark and existing estimators (approach 1) in both offline and online tests. This method has been deployed to production and is currently live in multiple cities all over the world.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257.10010258.10010259.10003268</concept_id>
<concept_desc>Computing methodologies~Ranking</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010321.10010333</concept_id>
<concept_desc>Computing methodologies~Ensemble methods</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003227</concept_id>
<concept_desc>Information systems~Information systems applications</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Ranking}
\ccsdesc[500]{Computing methodologies~Ensemble methods}
\ccsdesc[300]{Information systems~Information systems applications}

\keywords{Heterogeneous Treatment Effect; Causal Inference; User Retention; Optimization; Promotion}


\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
